---
title: "Assignment_4"
author: "deepak"
date: "2023-10-29"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("httr")
#install.packages("readr")
#install.packages("factoextra")
#install.packages("flexclust")
library(httr)
library(readr)
library(tidyverse)
library(factoextra)
library(ISLR)
library(flexclust)
library(caret)
```
#Importing Data set 
```{r}
#importing Data set and converting 
getwd()
pharma<-read.csv("C:/Users/durga/Downloads/Pharmaceuticals.csv")
#summarize the Data
#str(pharma)
head(pharma,10)
```
```{r}
set.seed(23)
#Data frame  Z Score scaling
pharma_scaled <- scale(pharma[,3:11])
summary(pharma_scaled)

# Data Frame Range Scaling 
pharma_range <- scale(pharma[,3:11])
```
a. Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in
conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s)
used, the number of clusters formed, and so on.
```{r}
set.seed(23)
dst_rows <- get_dist(pharma_scaled)
fviz_dist(dst_rows) #To visualize distance between matrix rows
cluster1 <- kmeans(pharma_scaled, centers = 3, nstart = 15) # HEre taking K=3 & nstart=15
fviz_cluster(cluster1, data = pharma_scaled)
print(cluster1)
```
The k-means algorithm was used to divide the 21 enterprises into three groups with no variable weights. We chose k=3 since that is the optimal k indicated by the silhouette approach.



```{r}
fviz_nbclust(pharma_scaled, kmeans, method = "wss") # WSS method (ELBOW METHOOD)

fviz_nbclust(pharma_scaled, kmeans, method = "silhouette") #SILHOUETTE Method (To find best K value)

```


b. Interpret the clusters with respect to the numerical variables used in forming the clusters.

I did not use the WSS approach since the graph did not show a distinct elbow and was extremely unclear. The graph does not indicate the elbow/knee position, and it flattens out more than once at k = 4 and 6, respectively, and I chose the silhouette approach since it is apparent to display the ideal cluster K = 5.

```{r}
#let's look at the mean value from actual data by clusters
aggregate(pharma[3:11], by=list(cluster=cluster1$cluster), mean) 
actual_data <- cbind(pharma, cluster = cluster1$cluster)
tibble(actual_data)
```
```{r}
by(actual_data, factor(actual_data$cluster), summary)#intensive statistical cluster analysis
```
Recommendations, Location and Exchange of cluster
```{r}
#Cluster median recommendation
T_Recom <- table(actual_data$cluster, actual_data$Median_Recommendation) 
names(dimnames(T_Recom)) <- c("Cluster", "Recommendation")
TR <- addmargins(T_Recom)
TR
```


The data do not show a clear link between clusterMedian Recommendation. There are 21 recommendations in total, with 1 strong buy, 7 moderate buys, 9 holds, and 4 moderate sells.
```{r}
#Cluster-based location breakdown
T_Location <- table(actual_data$cluster, actual_data$Location)
names(dimnames(T_Location)) <- c("Cluster", "Location")
Tlocation <- addmargins(T_Location)
Tlocation
```


We cannot deduce any association between cluster Location from the findings. A total of 21 firms are divided into 13 in the United States, three in the United Kingdom, and one each in Canada, France, Germany, Ireland, and Switzerland.
```{r}
#Exchange breakdown by cluster
T_Exchange <- table(actual_data$cluster, actual_data$Exchange)
names(dimnames(T_Exchange)) <- c("Cluster", "Exchange")
Texchange <- addmargins(T_Exchange)
Texchange
```
The results show that there is no link between clusterExchange. There are 21 corporations in all, divided into 1 Amex, 1 Nasdaq, and 19 NYSE.


c. Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in
forming the clusters)
```{r}
fviz_nbclust(pharma_range, FUN = kmeans, method = "silhouette")
fviz_nbclust(pharma_range, kmeans, method = "wss")
```
We also perform tests to determine the best k using range normalization. The ideal k is 2 from the silhouette and 6 from the elbow (not clear). We'll stick with z-score normalization data because the k from range normalization isn't as good.

d.Provide an appropriate name for each cluster using any or all of the variables in the dataset.
```{r}
set.seed(11)
cluster2 = kcca(pharma_scaled, k=3, kccaFamily("kmeans"))
cluster2
clusters(cluster2) 

#Apply the predict() function
clusters_index <- predict(cluster2)
image(cluster2)
points(pharma_scaled, col=clusters_index, pch=17, cex=1.0)
```
To run kmeans cluster on k =3, we use the kcca algorithm instead of kmeans from basic R.

```{r}
set.seed(11)
cluster2 = kcca(pharma_scaled, k=3, kccaFamily("kmedians"))
cluster2
clusters(cluster2) 

#Apply the predict() function
clusters_index <- predict(cluster2)
image(cluster2)
points(pharma_scaled, col=clusters_index, pch=16, cex=1.0)
```



a) Now that the clustering is complete, there are some insights we can pull from the output. Particularly, by using both the WSS and Silhouette methods, we could accurately determine that 5 clusters were needed as they both returned 5 as the optimum point. 


b) we can make some general inferences about the clusters: 

Cluster 1 had high ROE, ROA, Asset_Turnover, and Net_Profit_Margin, but low Market_Cap and Rev_Growth.
Cluster 2 had very high Beta and Leverage, but very low Market_Cap, ROE, ROA, Net_Profit_Margins_, and Revenue Growth, which is likely why is is the furthest away from cluster 4.
cluster 3 is the oddest of the bunch with only 2 members. This cluster has a VERY high PE_Ratio as well as a positive Asset_Turnover, but is low in every other category.
While having low leverage,Beta, and PE_Ratio: cluster 4 held high Market_cap, ROE, ROA, Asset_Turnover, Revenue Growth, and Net_Profit_Margin which together set it apart from its closest neighbor, cluster 1.
Cluster 5 has the a very high Rev_Growth and positive Beta and Leverage, while maintaining low numbers in the other categories. 


c) Looking at the last three columns that were not used in the clustering, there seems to be no consistent patterns within the clusters. Between most points, you will find that while they both may have the same exchange, the location or recommendation would be different, or visa versa. Though generally speaking, almost all were in the NYSE exchange anyways.

d) 
Cluster 1: Medium Market_cap,ROE,ROA,Asset_Turnover,Leverage, Net_Profit_Margin, and Rev_Growth: "Medium"
Cluster 2: very high Beta and Leverage, very low ROA and Net_Profit_Margin: "High beta, low assets"
Cluster 3: Extreme PE_Ratio and low Net_Profit_Margin:"High Price Earnings ratio, but low new profits"
Cluster 4: highest Market_Cap, ROE, ROA, Asset_Turnover, and Net_Profit_Margin: "great asset management with small negatives"
Cluster 5: small positive Beta with highest Rev_Growth and slightly negative Net_profit_margin: "bad asset management with good growth"
